Biogeography & Environmental Conditions Shape Phage & Bacteria Interaction Networks Across the Human Microbiome

### 2017-08-09 doc/manuscript.Rmd
Created doc with diffs highlighted.

![**Impact of Diet and Obesity on Gut Network Structure.** *(A) Quantification of average degree centrality (number of edges per node) and (B) closeness centrality (average distance from each node to every other node) of gut microbiome networks of subjects limited to exclusively high-fat or low-fat diets. Each point represents the centrality from a human subject stool sample that was collected 8-10 days following the beginning of their defined diet. There are five samples here, compared to the four in figure \ref{intradiv}, because one of the was only sampled post-diet, providing us data for this analysis but not allowing us to compare to a baseline for figure \ref{intradiv}. (C) Quantification of average degree centrality and (D) closeness centrality between obese and healthy adult women from the Twin gut study. Each point represents a stool sample taken from one of the three adult woman confirmed as obese or healthy and with matching virus and bacteria data. *\label{dietnetworks}](../figures/dietnetworks.pdf){ width=90% }

>>>>

![**Impact of Diet and Obesity on Gut Network Structure.** *(A) Quantification of average degree centrality (number of edges per node) and (B) closeness centrality (average distance from each node to every other node) of gut microbiome networks of subjects limited to exclusively high-fat or low-fat diets. Each point represents the centrality from a human subject stool sample that was collected 8-10 days following the beginning of their defined diet. There are five samples here, compared to the four in figure \ref{intradiv}, because one of the was only sampled post-diet, providing us data for this analysis but not allowing us to compare to a baseline for figure \ref{intradiv}. (C) Quantification of average degree centrality and (D) closeness centrality between obese and healthy adult women from the Twin gut study. Each point represents a stool sample taken from one of the three adult woman confirmed as obese or healthy and with matching virus and bacteria data.* \label{dietnetworks}](../figures/dietnetworks.pdf){ width=90% }
